---
title: "Writing Functions"
author: "Shaolei Ma"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
```

Set seed for reproducibility.

```{r}
set.seed(12345)
```

## Z score function

Z scores substract the mean and divide by the sd.

```{r}
x_vec = rnorm(20, mean = 5, sd = .3)
```

Compute Z scores for `x_vec`.

```{r}
(x_vec - mean(x_vec)) / sd(x_vec)
```

Write a function to do this!

```{r}
z_score = function(x){
  
  if(!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if (length(x) < 2) {
    stop("You need at lease 2 numbers to get z scores")
  }
  
  z = (x - mean(x)) / sd(x)
  
  z
  
}
```

Check that this works.

```{r}
z_score(x_vec)

z_score(x = rnorm(10, mean = 5))
```

Keep checking.

```{r, error = T}
z_score(x = 3)

z_score(c("my", "name", "is", "jeff"))

z_score(c(T, T, F, T))

z_score(iris)
```

## Multiple outputs.

Write a function that returns mean and standard deviation.

```{r}
mean_and_sd = function(x) {
  
  if(!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if (length(x) < 2) {
    stop("You need at lease 2 numbers to get means and sds")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Double check I did this right ..

```{r}
mean_and_sd(x_vec)
```

## Start getting means and sds

```{r}

x_vec = rnorm(n = 30, mean = 5, sd = .5)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)

```

Let's write a function that uses `n`, a true mean, and true SD as inputs.

```{r}
sim_mean_sd = function(n_obs, mu, sigma) {
  
  x_vec = rnorm(n = n_obs, mean = mu, sd = sigma)
  
  tibble(
    mean = mean(x_vec),
    sd = sd(x_vec)
  )
}

sim_mean_sd(n_obs = 30, mu = 5, sigma = .5)
```

## LoTR data

```{r}
import_LoTR = function(path = "data/LotR_Words.xlsx", movie_name, data_range) {
  
  movie_df =
    readxl::read_excel(path, range = data_range) |> 
    mutate(movie = movie_name) |> 
    janitor::clean_names() |> 
    pivot_longer(
      female:male,
      names_to = "sex",
      values_to = "words"
    ) |> 
    select(movie, everything())
  
  movie_df
  
}

lotr_tidy = import_LoTR(movie_name = "fellowship_ring", data_range = "B3:D6") |> 
  bind_rows(import_LoTR(movie_name = "two_towers", data_range = "F3:H6")) |> 
  bind_rows(import_LoTR(movie_name = "return_king", data_range = "J3:L6")) |> 
  mutate(race = str_to_lower(race))
```

## NSDUH

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

nsduh_table <- function(html, table_num, table_name) {
  
  table = 
    html |> 
    html_table() |> 
    nth(table_num) |>
    slice(-1) |> 
    select(-contains("P Value")) |>
    pivot_longer(
      -State,
      names_to = "age_year", 
      values_to = "percent") |>
    separate(age_year, into = c("age", "year"), sep = "\\(") |>
    mutate(
      year = str_replace(year, "\\)", ""),
      percent = str_replace(percent, "[a-c]$", ""),
      percent = as.numeric(percent),
      name = table_name) |>
    filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
}

nsduh_results = 
  bind_rows(
    nsduh_table(nsduh_html, 1, "marj_one_year"),
    nsduh_table(nsduh_html, 4, "cocaine_one_year"),
    nsduh_table(nsduh_html, 5, "heroin_one_year")
  )
```


```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)
```

